Notes: Complexity Lower Bound for Bayes Risks

### 2021-01-25 colt-21/cvx-flats.tex
A few minor notes/comments to self
Pre meeting, looking at narrative

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension that applies to both frameworks. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
%supervised learning blah
Surrogate risk minimization is one of the most widespread optimization heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to design a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.

We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction logarithmic in the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.\jessie{Some of this repetitive}

%in a seemingly unrelated setting, finance problems blah blah.
In its own line of literature, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessie{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
That is, institutions and individuals may only be expected to articulate predictions of summary statistics of their beliefs, rather than their entire belief.
To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
\jessie{Raf, helppp}

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
The two examples above are seemingly unrelated given how different the settings are; in the abstain problem, we have a finite prediction problem where we want to design a consistent convex surrogate for a given target loss.
In risk estimation, on the other hand, we aim to estimate a continuous variable based on the desired summary statistic instead of target loss.
These two types of problems have been historically studied with different mathematical tools because of these differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.

@@

\subsection{Consistency} \label{subsec:consistency}
\jessie{Looking at this now, sections 2.1-4 feel like a lot...}
\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.  Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.  This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
\jessie{Could split into high level in previous work; ie previous work and setting are distinct.}
\jessie{Top of 2 in setting}
\jessie{Want a clear distinction between what came before and what we're adding.}
\jessie{Can defer Lemma 8 to appendix?  Maybe}

@@

\paragraph{Our ``four quadrants'' of problem types}
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
\jessie{How does this paragraph change?}

@@

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}

@@

Throughout, given a distribution $p$ and set $P$ \jessiet{not necessarily a subspace, since $F$ isn't a subspace, but $P$ not necessarily convex...} $P$, we defined $P_p := P - \{p\}$ and $\Scr_P(p) := \spn(P_p)$.

>>>>

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central\jessiet{a tad dramatic?} importance, we give a new technique for constructing lower bounds on the convex prediction dimension that applies to both frameworks. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
%supervised learning blah
Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem.
Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
Depending on the data distribution, these inconsistent surrogates may actually yield high misprediction rates. \jessiet{Clean this up.}
%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question.

We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.\jessie{Some of this repetitive}

%in a seemingly unrelated setting, finance problems blah blah.
In its own line of literature, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessiet{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
That is, institutions and individuals might only be reasonably expected to articulate summary statistics of their beliefs, rather than their entire belief distribution.
To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
\jessie{Raf, helppp}

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
The two examples above are seemingly unrelated given how different the settings are; in the abstain problem, we have a finite prediction problem where we want to design a consistent convex surrogate for a given target loss.
In risk estimation, on the other hand, we aim to estimate a continuous variable based on the desired summary statistic instead of target loss.
These two types of problems have been historically studied with different mathematical tools because of these perceived differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.

@@

\subsection{Consistency} \label{subsec:consistency}
\jessiet{Looking at this now, sections 2.1-4 feel like a lot...}
\jessie{I think the story we want to tell is as follows: there are these two types of problems where [convex] prediction dimension is important.  Typically, these problems are studied with different tools; here, we present a tool to bound prediction dimension in both settings.  This tool relies on property elicitation, which we show (somehow for the first time to our knowledge) can be formally connected to consistency.}
\jessie{Could split into high level in previous work; ie previous work and setting are distinct.}
\jessie{Top of 2 in setting}
\jessie{Want a clear distinction between what came before and what we're adding.}
\jessie{Can defer Lemma 8 to appendix?  Maybe}

@@

\jessiet{I think we should move this paragraph to the intro?}
\paragraph{The ``four quadrants'' of problem types}
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
\jessie{How does this paragraph change?}
\jessie{Add image? tikz/consistency-elicitation-calibration.pdf}

@@

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \P, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}

@@

Throughout, given a distribution $p$ and set $P$ \jessiet{not necessarily a subspace, since $F$ isn't a subspace, but $P$ not necessarily convex...} $P$, we defined $P_p := P - \{p\}$ and $\Scr_P(p) := \spn(P_p)$.
\jessiet{Get rid of this notation?}
\jessiet{One extra step to show $\Sc_F(p) = \spn(F_p)$ maybe?}

### 2021-01-25 notes/raf-risk-lower-bound.tex
Pre meeting, looking at narrative

\begin{definition}
  \label{def:property}
  Let $\R$ be a nonempty set.
  A \emph{property} is a functional $\Gamma : \P \to 2^\R$.
%  When $|\R|$ is finite, we call $\Gamma$ a \emph{finite property}.
%  \raf{We only reference this in the discussion and appendix (mode for finite $\Y$); let's remove it from this main def.}
  The \emph{level set} $\Gamma_r \defeq \{p\in \P \,|\, r\in\Gamma(p)\}$ is the set of distributions $p$ corresponding to report value $r\in\R$.
  A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$. \jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}\raft{I'm not sure what you mean; check again?}
  When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.
\end{definition}

>>>>

\begin{definition}
  \label{def:property}
  Let $\R$ be a nonempty set.
  A \emph{property} is a functional $\Gamma : \P \to 2^\R$.
%  When $|\R|$ is finite, we call $\Gamma$ a \emph{finite property}.
%  \raf{We only reference this in the discussion and appendix (mode for finite $\Y$); let's remove it from this main def.}
  The \emph{level set} $\Gamma_r \defeq \{p\in \P \,|\, r\in\Gamma(p)\}$ is the set of distributions $p$ corresponding to report value $r\in\R$.
  A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
  We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$. \jessiet{Technically, $\range \Gamma = \bigcup_{p \in \P} \cup \Gamma(p)$, right?}\raft{I'm not sure what you mean; check again?}\jessiet{I was thinking about any value the property could possibly take, even if not uniquely, but I think that's wrong... feel free to delete/ignore this.}
  When $\R=\reals^d$ for some $d\in\N$, we write $\dim\Gamma = d$.
\end{definition}
